---
output:
  bookdown::pdf_document2:
    includes:
      before_body: Titlepage.tex
    fig_caption: yes
    number_sections: yes
    toc: no
    keep_tex: no
    latex_engine: xelatex
# citation_package: biblatex
# biblatexoptions: [refsegment=chapter]
bibliography: Bibliography.bib
csl: ../../Auxiliary/Haemophilia.csl
link-citations: true
urlcolor: black
linkcolor: black
fontsize: 12pt
geometry: margin = 1.2in
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \onehalfspacing
# - \usepackage[backend=biber, refsegment=chapter, defernumbers=true]{biblatex}
# - \addbibresource{Bibliography.bib}
---

```{r NHC_setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H")
```

\pagenumbering{arabic}

\newpage
\pagestyle{fancy}

\fancyhead[L,R]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headheight}{14.5pt}

\newpage
\renewcommand\contentsname{Table of contents}
\fancyhead[C]{Table of contents}
\setcounter{tocdepth}{3}
\tableofcontents


\newpage
\fancyhead[C]{Summary}

```{r child = 'Summary.Rmd'}
```

\newpage
\fancyhead[C]{Diagnosis}

```{r child = 'Diagnosis.Rmd'}
```

\newpage
\fancyhead[C]{Treatment of bleeding}

```{r child = 'Treatment.Rmd'}
```

\newpage
\fancyhead[C]{Eradication therapy}

```{r child = 'Eradication.Rmd'}
```

\newpage
\fancyhead[C]{References}

# References
