---
output:
  bookdown::pdf_document2:
    includes:
      before_body: Titlepage.tex
    fig_caption: yes
    number_sections: no
    toc: no
    keep_tex: no
    latex_engine: xelatex
# citation_package: biblatex
# biblatexoptions: [refsegment=chapter]
bibliography: Bibliography.bib
csl: ../Auxiliary/Haemophilia.csl
link-citations: true
urlcolor: black
linkcolor: black
fontsize: 12pt
geometry: margin = 1.2in
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \onehalfspacing
# - \usepackage[backend=biber, refsegment=chapter, defernumbers=true]{biblatex}
# - \addbibresource{Bibliography.bib}
---

```{r NHC_setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H")
```

\pagenumbering{arabic}

\newpage
\pagestyle{fancy}

\fancyhead[L,R]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headheight}{14.5pt}

\newpage
\renewcommand\contentsname{Table of contents}
\fancyhead[C]{Table of contents}
\setcounter{tocdepth}{3}
\tableofcontents

\newpage
\fancyhead[C]{Authors}

```{r child = 'Authors.Rmd'}
```

\newpage
\fancyhead[C]{History of hemophilia in the Nordic countries}

```{r child = 'History.Rmd'}
```

\newpage
\fancyhead[C]{Organisation of hemophilia care}

```{r child = 'Organization.Rmd'}
```

<!-- \printbibliography[segment=\therefsegment,heading=subbibliography] -->

\newpage
\fancyhead[C]{Laboratory diagnosis}

```{r child = 'Lab.Rmd'}
```

\newpage
\fancyhead[C]{Prophylaxis and on demand treatment}

```{r child = 'Treatment.Rmd'}
```

\newpage
\fancyhead[C]{Adolescence}

```{r child = 'Adolescence.Rmd'}
```

\newpage
\fancyhead[C]{Inhibitors}

```{r child = 'Inhibitors.Rmd'}
```

\newpage
\fancyhead[C]{Surgery in hemophilia - practical guidelines}

```{r child = 'Surgery.Rmd'}
```

\newpage
\fancyhead[C]{Surgery in PWHs with inhibitors}

```{r child = 'SurgeryInhibitors.Rmd'}
```

\newpage
\fancyhead[C]{Comorbidities in the ageing patients with hemophilia}

```{r child = 'Comorbidities.Rmd'}
```

\newpage
\fancyhead[C]{Treatment of pain}

```{r child = 'Pain.Rmd'}
```

\newpage
\fancyhead[C]{Physiotherapy}

```{r child = 'Physiotherapy.Rmd'}
```

\newpage
\fancyhead[C]{Carriers of haemophilia}

```{r child = 'Carriers.Rmd'}
```

\newpage
\fancyhead[C]{Hemophilia nurse functions}

```{r child = 'Nursing.Rmd'}
```

\newpage
\fancyhead[C]{Dental care}

```{r child = 'Dental.Rmd'}
```

\newpage
\fancyhead[C]{References}

# References
